---
title: "Innovations"
format: 
  dashboard:
    logo: "images/CGIAR.png"
    orientation: columns

---


```{r}
#| message: false
library(tidyverse)
library(httr2)
library(sf)
library(leaflet)
library(gt)

```


# Rice - Boro







## Column

### Row 

```{r}
#| component: valuebox
#| title: Latest Adoption Estimates
list(
  icon = "calendar-week",
  color = "dark",
  value = 2018
)
```

```{r}
#| component: valuebox
#| title: Share of Boro Area - CGIAR-derived varieties
list(
  icon = "pin-map",
  color = "dark",
  value = "67%"
)
```

### Row

<style>
/* Custom Table Styling */
.custom-table {
  background-color: black; /* Black background */
  border-collapse: collapse;
  width: 100%;
  margin: 20px 0;
  font-size: 1rem;
  color: white; /* White text */
}

.custom-table th {
  background-color: #333; /* Dark gray for header */
  color: white;
  text-align: left;
  padding: 8px;
}

.custom-table th, .custom-table td {
  border: 1px solid #555; /* Dark gray border */
  padding: 8px;
}

.custom-table tr:nth-child(even) {
  background-color: #222; /* Slightly lighter black for alternating rows */
}

.custom-table tr:hover {
  background-color: #444; /* Dark gray highlight on hover */
}
</style>

<table class="custom-table">
   <caption style="color: white; font-weight: bold;">* This survey is non-representative. Furthermore, the North-western region of Bangladesh is very drought prone, and was therefore the target of AWD dissemination throughout the years. Adoption rates are therefore likely to be overestimated by these figures.</caption>
   <thead>
      <tr>
         <th>Innovation</th>
         <th>Description</th>
         <th>Best Reach Estimate</th>
         <th>Source</th>
         <th>Attribution</th>
      </tr>
   </thead>
   <tbody>
      <tr>
         <td>BRRI dhan-28 (1994)</td>
         <td>High yield advantage, Early maturing</td>
         <td>Covered 32.9% of Boro rice area</td>
         <td>BIHS 2018</td>
         <td>1 IRRI line as parent</td>
      </tr>
      <tr>
         <td>BRRI dhan-29 (1994)</td>
         <td>High yield advantage, Disease resistant</td>
         <td>Covered 29.3% of Boro rice area</td>
         <td>BIHS 2018</td>
         <td>Other IRRI ancestry</td>
      </tr>
      <tr>
         <td>Other IRRI-derived varieties</td>
         <td>Residual share of Boro plots cultivated with minor varieties that have some IRRI ancestry</td>
         <td>Covered 4.86% of Boro rice area</td>
         <td>BIHS 2018</td>
         <td>Between those with one and two IRRI parents<br>+ those with other IRRI ancestry</td>
      </tr>
      
         <tr>
         <td>Alternate Wetting and Drying</td>
         <td>Water-saving irrigation technique where rice fields are periodically flooded and allowed to dry, reducing water usage while maintaining crop yields.</td>
         <td>In a sample of farmers in north-western Bangladesh, 21.3 % farm households had adopted AWD during the Boro season * </td>
         <td><a href="https://www.sciencedirect.com/science/article/pii/S026483771931868X#:~:text=However%2C%20AWD%20adoption%20in%20Bangladesh,diffusion%20of%20water%2Dsaving%20technologies." target="_blank">Alauddin et al, 2020</a></td>
         <td>Between those with one and two IRRI parents<br>+ those with other IRRI ancestry</td>
      </tr>
   </tbody>
</table>



## Column


### Row {height="40%" .tabset}

#### BRRI dhan-28

Oi


#### BRRI dhan-29

Oi




# Rice - Aman {orientation="columns"}




# Fish {orientation="columns"}




# Lentils {orientation="columns"}



# Maize {orientation="columns"}


# Wheat {orientation="columns"}


# Potatos {orientation="columns"}

# Mechanization {orientation="columns"}